Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda \\~

### 2013-03-11 Web3D2013-Dec3D/paper.tex
req update

Polyfill-based approaches allow deriving hard requirements for related and utilized W3C standards and user agent APIs immediately. This leads to much more evolving concepts and solutions in contrast to an overall declarative 3D specification.
To sum up, the X3DOM and XML3D experimental declarative 3D Web publishing frameworks are designed to explore different options for adding 3D graphics to HTML. Here, Figure \ref{fig:polyArch} depicts our proposed declarative 3D polyfill runtime architecture, though we'd like to stress that the whole integration model is still evolving and open for discussion.

>>>>

Polyfill-based approaches allow deriving hard requirements for related and utilized W3C standards and user agent APIs immediately.

\begin{description}
\item[DOM] The Layer must be able to access and monitor changes in related DOM elements. This is currently achieved using the DOM Level 2 MotationEvents but may build on the new MutationObserver 
\item[Events] The UA must support registration, firing and extending UI-Events. This is mainly done through dynamic property changes in the JavaScript object which represents the Event today
\item[Custom CSS properties] The goal is to support scene management though custom CSS properties. This was not possible thought the last years but my change with the new CSS Custom Properties specification \cite{CSSCustom}. 
\item[CSS 3D Transform] CSS 3D Transforms module is now supported in all major browser. The methods to monitor final matrix changes are limited right now and should be extended for optimal performance 
\item[TypedArrays] TypedArrays where first introduces with the WebGL specification but are now a established method to process large portions of typed data efficiently.    
\item[Generic GPU access] For client side rendering the Polyfill layer has to access the GPU functionally almost directly. WebGL is there a perfect candidate and Flash/Stag3D a second option. 
\end{description}

This leads to much more evolving concepts and solutions in contrast to an overall declarative 3D specification.
To sum up, the X3DOM and XML3D experimental declarative 3D Web publishing frameworks are designed to explore different options for adding 3D graphics to HTML. Here, Figure \ref{fig:polyArch} depicts our proposed declarative 3D polyfill runtime architecture, though we'd like to stress that the whole integration model is still evolving and open for discussion.
